### 2013-01-19 edupar-13/outcomes.tex
outcomes.tex: Trivial drive-by text squeezings.

At approximately the mid-point of the semester,
thirty-nine thread-library projects were submitted
on behalf of thirty-eight two-person teams and one
auditing student who was working solo.
%
Submitted thread libraries were 800 lines of C code
and 50 lines of x86 assembly-language code,
though some were half that size and some were triple.
%
At this point, three teams dropped and the auditing
student's requirements were complete;
also, four teams fragmented---some students dropped and
two new teams emerged.
Thus, thirty-three teams attempted the kernel project.
%
Twenty-four teams submitted kernels on time and nine
teams were forced to take extra time to complete the
kernel project.
Most kernels ranged in size from 2,500 to 3,500 lines
of C code and 100 to 400 lines of assembly code,
though some submissions were roughly twice as large
(late kernels and on-time kernels were essentially the
same size).

@@

The symmetric-multiprocessing kernel-extension project
was a mixed success.
Of the twenty-four teams that attempted it,
one solo team was unable to submit a solution.
Nineteen of the remaining twenty-three groups
completed part of the project---at least enough to
boot multiple cores (one, two, or eight depending
on the simulator configuration) into their scheduler.
Four of those nineteen groups were able to run
almost all of our test suite of simple multi-threaded
applications.
Seven more groups were able to run roughly half of
the combinations of core counts versus test applications.
Finally, it was the sense of the grading team that
most groups would have been able to substantially complete
the project given a further week of development time.
We view this outcome as an indication that feasible adjustments
to the course design would bring this material within reach
of most students.

>>>>

At approximately the mid-point of the semester,
thirty-nine thread-library projects were submitted
on behalf of thirty-eight two-person teams and one
auditing student who was working solo.
%
Submitted thread libraries were roughly 800 lines of C code
and 50 lines of x86 assembly-language code,
though some were half that size and some were triple.
%
At this point, three teams dropped and the auditing
student's requirements were complete;
also, four teams fragmented---some students dropped and
two new teams emerged.
Thus, thirty-three teams attempted the kernel project.
%
Twenty-four teams submitted kernels on time and nine
teams were forced to take extra time to complete the
kernel project.
Most kernels ranged in size from 2,500 to 3,500 lines
of C code and 100 to 400 lines of assembly code,
though some submissions were roughly twice as large
(late kernels and on-time kernels were essentially the
same size).

@@

The SMP kernel-extension project
was a mixed success.
Of the twenty-four teams that attempted it,
one solo team was unable to submit a solution.
Nineteen of the remaining twenty-three groups
completed part of the project---at least enough to
boot multiple cores
\shortversion{}{(one, two, or eight depending on the simulator configuration)}
into their scheduler.
Four of those nineteen groups were able to run
almost all of our test suite of simple multi-threaded
applications.
Seven more groups were able to run roughly half of
the combinations of core counts versus test applications.
Finally, it was the sense of the grading team that
most groups would have been able to substantially complete
the project given a further week of development time.
We view this outcome as an indication that feasible adjustments
to the course design would bring this material within reach
of most students.
